# Objective

+ Create monthly nitrogen-corn price ratio data from 2002 to 2022

## Preparation

```{r}
# === Packages ===#
library(data.table)
library(tidyverse)
library(tidyr)
library(dplyr)
library(magrittr)
library(stringr)
library(ggplot2)
library(ggpubr)
library(here)
options(stringsAsFactors = FALSE)
```

## Load raw data

**NASS_fertilizer_price_yearly.csv**

+ source: NASS Quick Stat -> Survey -> Economics -> Prices Paid -> Nitrogen -> Price Paid
+ temporal resolution: yearly
+ period: 2002-2014

**NASS_fertilizer_index.csv**

+ source: NASS Quick Stat -> Survey -> Economics -> Prices Paid -> Nitrogen -> INDEX FOR PRICE PAID, 2011
+ temporal resolution: monthly
+ period: 1990-2022

**NASS_corn_price.csv**

+ source: NASS Quick Stat -> Survey -> Crops -> Field Crops -> Corn -> PRICE RECEIVED -> CORN, GRAIN - PRICE RECEIVED, MEASURED IN $ / BU
+ temporal resolution: monthly
+ period: 1908-2022

**DTN Fertilizer Trends_weekly.csv**

+ source: Quinn, R. (2022, March 2). DTN Retail Fertilizer Trends. DTN- Progressive Farmer. https://www.dtnpf.com/agriculture/web/ag/crops/article/2022/03/02/average-retail-fertilizer-prices
+ temporal resolution: weekly
+ period: 1908-2022

```{r}
#* corn price (1908-2022, monthly)
NASS_corn_monthly <-
  read.csv(here("Shared/Data/price_data/NASS_corn_price_monthly.csv")) %>%
  data.table() %>%
  .[, .(Year, Period, Value)] %>%
  .[Period != "MARKETING YEAR", ] %>%
  setnames("Value", "pCorn") %>%
  # === unit conversion: $/bushel to $/kg
  .[, pCorn := pCorn / 25.4] %>%
  print()

#* N fertilizer price (2002-2014, yearly)
NASS_N_yearly <-
  read.csv(here("Shared/Data/price_data/NASS_fertilizer_price_yearly.csv")) %>%
  data.table() %>%
  .[, .(Year, Data.Item, Value)] %>%
  setnames(c("Data.Item", "Value"), c("N_type", "pN")) %>%
  .[str_detect(N_type, "ANHYDROUS AMMONIA"), N_type := "ANHYD"] %>%
  .[str_detect(N_type, "28%"), N_type := "UAN28"] %>%
  .[str_detect(N_type, "32%"), N_type := "UAN32"] %>%
  # === convert to wide format
  dcast(Year ~ N_type, value.var = "pN") %>%
  # === unit conversion: raw $/ton to pure $/kg N
  .[, ANHYD := ANHYD / (2000 * 0.82) / 0.453592] %>%
  .[, UAN28 := UAN28 / (2000 * 0.28) / 0.453592] %>%
  .[, UAN32 := UAN32 / (2000 * 0.34) / 0.453592] %>%
  print()

#* N fertilizer price (2015-2022, weekly)
DTN_N_weekly <-
  read.csv(here("Shared/Data/price_data/DTN Fertilizer Trends_weekly.csv")) %>%
  data.table() %>%
  .[, Year := substr(Date.Range, nchar(Date.Range) - 3, nchar(Date.Range))] %>%
  .[, Week := substr(Date.Range, 1, nchar(Date.Range) - 5)] %>%
  .[, Month := substr(Date.Range, 1, 3)] %>%
  .[, Date.Range := NULL] %>%
  .[, Year := as.numeric(Year)] %>%
  .[, ANHYD := as.numeric(ANHYD)] %>%
  .[, UAN28 := as.numeric(UAN28)] %>%
  .[, UAN32 := as.numeric(UAN32)] %>%
  # === unit conversion: raw $/ton to pure $/kg N
  .[, ANHYD := ANHYD / (2000 * 0.82) / 0.453592] %>%
  .[, UAN28 := UAN28 / (2000 * 0.28) / 0.453592] %>%
  .[, UAN32 := UAN32 / (2000 * 0.34) / 0.453592] %>%
  print()
```

## Combine and build monthly data set

+ corn price: NASS monthly (2002-2022)
+ N price: NASS yearly (2002-2014) + DTN weekly (2015-2022)
+ N types: (ANHYD, UAN28, UAN32)

```{r}
#* month name data table
month_name <-
  data.table(
    Period = c(
      "JAN", "FEB", "MAR", "APR", "MAY", "JUN",
      "JUL", "AUG", "SEP", "OCT", "NOV", "DEC"
    ),
    Month = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12)
  )

#* pseudo monthly NASS N prices (2002-2014)
(
  NASS_N_monthly <-
    NASS_N_yearly %>%
    expand_grid(., month_name) %>%
    data.table()
)

#* monthly DTN N data (2015-2022)
(
  DTN_N_monthly <-
    DTN_N_weekly %>%
    dplyr::select(Year, Month, ANHYD, UAN28, UAN32) %>%
    # === aggregate weekly data to monthly
    .[, lapply(.SD, mean),
      .SDcols = c("ANHYD", "UAN28", "UAN32"),
      by = .(Year, Month)
    ] %>%
    .[, Month := toupper(Month)] %>%
    setnames("Month", "Period") %>%
    merge(., month_name, by = "Period")
)


#* N:Corn price ratio data
(
  price_ratio_data <-
    # === combine NASS and DNT data
    rbind(NASS_N_monthly, DTN_N_monthly) %>%
    # === merge corn price
    merge(NASS_corn_monthly, ., by = c("Year", "Period")) %>%
    # === convert to long format
    melt(id.vars = c("Year", "Period", "Month", "pCorn")) %>%
    setnames(c("variable", "value"), c("Ntype", "pN")) %>%
    # === price ratio
    .[, pRatio := pN / pCorn]
)

saveRDS(price_ratio_data, file = here("Shared/Data/price_ratio_data.rds"))
```

## Summary and graphing

```{r}
price_ratio_data <- readRDS(here("Shared/Data/price_ratio_data.rds"))
```

### summary statistics

```{r}
# corn price
# price_ratio_data$pCorn %>% quantile(na.rm = TRUE)
# N price (pool ANHYD, UAN28, UAN32 together)
# price_ratio_data$pN %>% quantile(na.rm = TRUE)
# price ratio (pool ANHYD, UAN28, UAN32 together)
price_ratio_data$pRatio %>% quantile(na.rm = TRUE, prob = c(0.05, 0.25, 0.5, 0.75, 0.95))
```

